\documentclass{resume}

\rohead{\thepage\ of \pageref{LastPage}}

\begin{document}

\moveleft.5\hoffset\centerline{\large\bf Dina Yerlan}
\moveleft.5\hoffset\centerline{dyerlan@andrew.cmu.edu|412.515.7698|dinayerlan.me}
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip



\section{Education}




\section{Skills}

\stdtable{
Languages  & \emph{Professional}: PHP, JavaScript, Python, SQL\\
           & \emph{Hobby/Education}: Clojure, \LaTeX, C, C\#, C++, C, Java\\
Tools      & Tesseract, OpenCV, Silex, Symfony2, Doctrine2, Backbone.js, node.js, socket.io\\
Services   & Amazon S3, Rackspace CloudFiles, Stripe, PayPal\\
           & \emph{APIs}: Twitter, Facebook, LinkedIn, YouTube, Google Analytics\\
DBs        & MySQL, MongoDB, neo4j, SQL Server\\
}

\section{Relevant Experience}

\employer
	{CROSCON}
	{http://croscon.com/}
	{May 2013 --- \emph{Present}}
	{Senior Engineer}
	{Lead team of software developers to glorious victory in battle.}
\\ \\ \\
\employer
	{Splash Media}
	{http://splashmedia.com/}
	{February 2012 --- May 2013}
	{Software Wizard}
	{Core developer of \href{http://splashcube.com/}{SplashCube}, \href{http://splashmediau.com/}{Splash Media U} and other initiatives. Maintained server infrastructure consuming data from 5 social networks on anywhere from an hourly to a near-realtime basis for hundreds of accounts, utilizing queue-based architectures to increase throughput and resiliency. Helped implement and maintain bleeding-edge techniques for clean and high quality codebases, from Composer, Vagrant, and Puppet for consistent developer environments; to Fabric for deployment automation. Refactored front-end to use Backbone.js and developed streaming services and consumption using node.js and socket.io.}
\\ \\ \\
\employer
	{RAPP}
	{http://rapp.com}
	{March 2011 --- January 2012}
	{Interactive Software Engineer}
	{Co-lead architect \& developer for high profile website. Built an interactive movie memory wall \& kiosk using \href{http://flask.pocoo.org/}{Flask} (Python), HTML \& JavaScript for AMC Theatres for use in booths at public events such as their Comicon San Deigo after-party and the \href{http://www.accesshollywood.com/backstage-at-the-emmys/emmys-2011-backstage-at-the-hp-touchsmart-gift-lounge-day-1_gallerytab_3129/20}{2011 Emmy Awards}.}
\\ \\ \\
\employer
	{Moverati}
	{http://moverati.com}
	{September 2010 --- March 2011}
	{Developer}
	{Develop and maintain web presence using Zend Framework, Symfony DI, and Doctrine 2.0. Helped migrate storage to Amazon S3. Maintained front-end interactivity with jQuery and Facebook connect. Ensured site scaled with spikes in traffic during events such as the NFL Superbowl Experience 2011.}
\\ \\ \\
\employer
	{Orthochronos Forecasting, LLC.}
	{http://orthochronos.com/}
	{July 2009 --- July 2011}
	{Consultant}
	{Built and maintained original application, retained for maintenance and upgrades. Implemented PayPal recurring billing and a Python data import daemon.}
\\ \\ \\
\employer
	{Texas A\&M Division of Student Affairs Department of IT}
	{http://doit.tamu.edu/}
	{April 2009 --- September 2010}
	{Senior Software Applications Developer}
	{Developed Zend Framework and Doctrine 1.x applications. Developed Python daemon to import student information and provided via JSON API.}
\\ \\
\emph{Full employment history available upon request\ldots}

\section{Selected Open Source Contributions}

\project
	{Phorever}
	{https://github.com/dcousineau/phorever}
	{Creator}
	{PHP daemon and long-running process management, built to address a need internally at Splash Media and released as open source.}
\\ \\ \\
\project
	{Spaz / SpazHD for HP WebOS}
	{http://getspaz.com/}
	{\small{(Former)} \normalsize{Contributor}}
	{A fully open-source twitter client for HP WebOS devices including the TouchPad. Contributed to maintenence when Twitter introduced PIN authentication, worked on low-level Enyo performance, and served as a rep by attending WebOS developer days.}


\section{Community \& Awards}

Co-Organizer \& Founder of \href{http://queensjs.com/}{QueensJS}, former \href{http://www.meetup.com/dallasphp/}{DallasPHP} co-organizer
\\
Co-Organizer of the \href{http://lonestarphp.com/}{Lone Star PHP 2012, 2013, \& 2014 Conference}
\\
Eagle Scout Rank, Boy Scouts of America, 2004

\section{Education}

\stdtable{
School              & Texas A\&M University \hfill Class of 2009\\
Degree              & B.S., Computer Science; Minor, Business Administration\\
}

\end{document}
